% !TEX TS-program = XeLaTeX
% !TEX encoding = UTF-8 Unicode



\documentclass[12pt, a4paper, openany, twoside]{book}

% 字体配置文件
%%%for macOS 字体
% \input{setup/fonts}
%%%for office windows字体
 \input{setup/windows_fonts}

% 宏包配置文件
\input{setup/packages}

% 格式文件
\input{setup/format_note_book}  %XeLaTeX笔记本模板
\input{setup/code_style}  %代码块格式
\begin{document}

% 定义所有的图片文件在 FIGURES_thermal 子目录下
\graphicspath{{FIGURES/}}

% 前言
\frontmatter
\pagenumbering{Roman}


% 设置目录字体和行间距
\defaultmenufont
% 目录
\tableofcontents
\cleardoublepage
% 插图目录
%\listoffigures
% 表格目录
%\listoftables
\cleardoublepage

\defaultfont
\mainmatter
% 正文章节
\defaultfont
\renewcommand{\thefootnote}{\arabic{footnote}}



\include{body/ROM}



\cleardoublepage


% 参考文献
\defaultfont
\wuhao


\begin{thebibliography}{99}
\bibitem{Ruppert}Ruppert J. A Delaunay refinement algorithm for quality 2-dimensional mesh generation[J].
\bibitem{Shewchuk}Cheng S W, Dey T K, Shewchuk J, et al. Delaunay mesh generation[M].
\bibitem{Chew}L. Paul Chew. Guaranteed-Quality Mesh Generation for Curved Surfaces.
\bibitem{Üngör}Üngör A. Off-centers: A new type of Steiner points for computing size-optimal quality-guaranteed Delaunay triangulations[C]//Latin American Symposium on Theoretical Informatics. Berlin, Heidelberg: Springer Berlin Heidelberg, 2004: 152-161.
\bibitem{OVM}Kremer M, Bommes D, Kobbelt L. OpenVolumeMesh–A versatile index-based data structure for 3D polytopal complexes[C]//Proceedings of the 21st International Meshing Roundtable. Springer Berlin Heidelberg, 2013: 531-548.
\bibitem{CompGeo}De Berg M. Computational geometry: algorithms and applications[M]. Springer Science \& Business Media, 2000.
\bibitem{LEDA}Mehlhorn K, Näher S. LEDA: A platform for combinatorial and geometric computing[M]. Cambridge university press, 1999.
\bibitem{CDT-Zalik}Domiter V, Žalik B. Sweep‐line algorithm for constrained Delaunay triangulation[J]. International Journal of Geographical Information Science, 2008, 22(4): 449-462.
\end{thebibliography}

\cleardoublepage



\cleardoublepage

\end{document}
